---
title: "Fibroblasts subclustering including Ganciclovir samples"
author: "GinoBonazza (ginoandrea.bonazza@usz.ch)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: inline
---

```{r knitr config, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(warning = FALSE)

knitr::opts_chunk$set(message = FALSE)

knitr::opts_chunk$set(cache = FALSE)

knitr::opts_chunk$set(dpi = 300, fig.align = "center")
```

## Setup

```{r setup, class.source = "fold-hide"}
# Get current file name to make folder
current_file <- "Fibroblasts_subclustering_Ganciclovir"

# Load libraries
library(here)
library(readr)
library(readxl)
library(xlsx)
library(Seurat)
library(DropletUtils)
library(Matrix)
library(scDblFinder)
library(scCustomize)
library(dplyr)
library(ggplot2)
library(magrittr)
library(harmony)
library(tidyverse)
library(reshape2)
library(S4Vectors)
library(SingleCellExperiment)
library(pheatmap)
library(png)
library(gridExtra)
library(knitr)
library(scales)
library(RColorBrewer)
library(Matrix.utils)
library(tibble)
library(ggplot2)
library(scater)
library(patchwork)
library(statmod)
library(ArchR)
library(clustree)
library(gprofiler2)
library(clusterProfiler)
library(org.Mm.eg.db)
library(AnnotationHub)
library(ReactomePA)
library(speckle)
library(statmod)
library(reactable)

#Output paths
output_dir_data <- here::here("output", current_file)
if (!dir.exists(output_dir_data)) dir.create(output_dir_data)

if (!dir.exists(here::here("docs", "figure"))) dir.create(here::here("docs", "figure"))

output_dir_figs <- here::here("docs", "figure", paste0(current_file, ".Rmd"))
if (!dir.exists(output_dir_figs)) dir.create(output_dir_figs)
```

Load dataset and subset fibroblasts

```{r Load data, eval = FALSE}
FB <- readRDS(here::here("output", "QC_integration_annotation_Ganciclovir", "EAM_integrated.rds"))
FB <- subset(FB, cell_type == "Fibroblasts")
table(FB$Sample)
```

Re-scale the subsetted object

```{r Rescale, eval=FALSE}
DefaultAssay(FB) <- "RNA"
FB <- FB %>%
    FindVariableFeatures(selection.method = "vst", nfeatures = 3000) %>% 
    ScaleData(features = rownames(FB), vars.to.regress = "percent.mt")
```

PCA

```{r RunPCA, eval=FALSE, include=FALSE}
FB <- RunPCA(FB, npcs = 50)
```

```{r save FB, eval = FALSE}
saveRDS(FB, 
        here::here(output_dir_data, "FB.rds"))
```

```{r read FB}
FB <- readRDS(here::here(output_dir_data, "FB.rds"))
```

```{r Elbow_FB, fig.width=4, fig.height=4}
ElbowPlot(FB, ndims = 50)
```

Reintegrate the samples using Harmony

```{r RunHarmony, eval=FALSE}
FB <- RunHarmony(FB, assay.use="RNA", group.by.vars = "Sample", dims.use = 1:50)
```

Clustering

```{r Clustering, eval=FALSE}
FB <- RunUMAP(FB, dims = 1:30, reduction = "harmony")
FB <- FindNeighbors(FB, dims = 1:30, reduction = "harmony")
FB <- FindClusters(FB, resolution = seq(0.1, 0.8, by=0.1))
```

```{r Clustree_FB, fig.width=6, fig.height=9}
clustree::clustree(FB@meta.data[,grep("RNA_snn_res", colnames(FB@meta.data))],
                   prefix = "RNA_snn_res.")
```

```{r UMAPs_FB, fig.width=14, fig.height=4}
DimPlot(FB, reduction = "umap", shuffle = T,
        group.by = c("RNA_snn_res.0.1", "Sample", "Group"), ncol = 3)
```

Find the markers that characterize each cell population

Find the markers that characterize each cell population

```{r FindAllMarkers}
DefaultAssay(FB) <- "RNA"
Idents(FB) <- "RNA_snn_res.0.1"
Markers <- FindAllMarkers(FB, only.pos = TRUE, min.pct = 0.5, logfc.threshold = 0.5)
write.csv(Markers, here::here(output_dir_data, "FB_Markers_all.csv"))
Markers_top10 <- as.data.frame(Markers %>% group_by(cluster) %>% top_n(n = 10, wt = avg_log2FC))
write.csv(Markers_top10, here::here(output_dir_data, "FB_Markers_top10.csv"))
Markers_top3 <- as.data.frame(Markers %>% group_by(cluster) %>% top_n(n = 3, wt = avg_log2FC))
write.csv(Markers_top3, here::here(output_dir_data, "FB_Markers_top3.csv"))
reactable(Markers, 
          filterable = TRUE,
          searchable = TRUE,
          showPageSizeOptions = TRUE)
```

```{r Heatmap_FB, fig.width=15, fig.height=10}
mapal <- colorRampPalette(RColorBrewer::brewer.pal(9,"RdBu"))(256)
mapal <- rev(mapal[1:256])
Heatmap <- DoHeatmap(FB, draw.line = F, features = Markers_top10$gene) +
  scale_fill_gradientn(colours = mapal) +
  theme(text = element_text(size = 15), axis.text.y = element_text(size = 7)) +
  theme(plot.margin = unit(c(0.1, 0, 0, 0), 
                           "inches"))
Heatmap
```


## Cell type annotation

Annotate the clusters based on the characteristic markers

```{r, eval=FALSE}
FB@meta.data[FB@meta.data$RNA_snn_res.0.1 %in% c("0"), "cell_state"] = "FB1"
FB@meta.data[FB@meta.data$RNA_snn_res.0.1 %in% c("1"), "cell_state"] = "FB2"
FB@meta.data[FB@meta.data$RNA_snn_res.0.1 %in% c("2"), "cell_state"] = "FB3"
FB@meta.data[FB@meta.data$RNA_snn_res.0.1 %in% c("3"), "cell_state"] = "Epicardial cells"
FB@meta.data[FB@meta.data$RNA_snn_res.0.1 %in% c("4"), "cell_state"] = "FB4"
FB@meta.data[FB@meta.data$RNA_snn_res.0.1 %in% c("5"), "cell_state"] = "Neuronal cells"

FB$cell_state <- factor(FB$cell_state, levels = c("FB1", "FB2", "FB3", "Epicardial cells", "FB4","Neuronal cells"))
Idents(FB) <- FB$cell_state
```

```{r UMAP_cell_state_neuro_epi, fig.width=6.5, fig.height=6}
p <- DimPlot(FB, group.by = "cell_state", reduction = "umap", label = F) + 
  NoLegend() + 
  theme(axis.text=element_text(size=10, face = "bold"), axis.title = element_text(size = 14, face = "bold")) + 
  theme(plot.title = element_blank())
LabelClusters(p, id = "cell_state", fontface = "bold", size = 7, repel = T)
```

```{r save FB_2, eval = FALSE}
saveRDS(FB, 
        here::here(output_dir_data, "FB.rds"))
```

Remove neuronal and epicardial cells

```{r subset neuro}
FB <- subset(FB, cell_state %in% c("FB1", "FB2", "FB3", "FB4"))
FB$cell_state <- factor(FB$cell_state, levels = c("FB1", "FB2", "FB3","FB4"))
Idents(FB) <- FB$cell_state
```

```{r FindAllMarkers cell_state}
DefaultAssay(FB) <- "RNA"
Idents(FB) <- "cell_state"
Markers <- FindAllMarkers(FB, only.pos = TRUE, min.pct = 0.5, logfc.threshold = 0.5)
write.csv(Markers, here::here(output_dir_data, "EAM_Markers_all_cell_state.csv"))
Markers_top25 <- as.data.frame(Markers %>% group_by(cluster) %>% top_n(n = 25, wt = avg_log2FC))
write.csv(Markers_top25, here::here(output_dir_data, "EAM_Markers_top25_cell_state.csv"))
Markers_top10 <- as.data.frame(Markers %>% group_by(cluster) %>% top_n(n = 10, wt = avg_log2FC))
write.csv(Markers_top10, here::here(output_dir_data, "EAM_Markers_top10_cell_state.csv"))
Markers_top3 <- as.data.frame(Markers %>% group_by(cluster) %>% top_n(n = 3, wt = avg_log2FC))
write.csv(Markers_top3, here::here(output_dir_data, "EAM_Markers_top3_cell_state.csv"))
Markers_FB3 <- as.data.frame(Markers %>% group_by(cluster) %>% dplyr::filter(cluster == "FB3"))
write.csv(Markers_FB3, here::here(output_dir_data, "EAM_Markers_FB3.csv"))
reactable(Markers, 
          filterable = TRUE,
          searchable = TRUE,
          showPageSizeOptions = TRUE)
```

```{r Heatmap_cell_state, fig.width=12, fig.height=8}
Heatmap <- DoHeatmap(FB, draw.line = F, features = Markers_top10$gene) + 
  scale_fill_gradientn(colours = mapal) +
  theme(text = element_text(size = 15), 
        axis.text.y = element_text(size = 8)) +
  theme(plot.margin = unit(c(0.1, 0, 0, 0), "inches")) +
  guides(fill = guide_colorbar(barwidth = 1, barheight = 4))
Heatmap
```

```{r UMAP_cell_state, fig.width=6.5, fig.height=6}
p <- DimPlot(FB, group.by = "cell_state", reduction = "umap", label = F) + 
  NoLegend() + 
  theme(axis.text=element_text(size=10, face = "bold"), axis.title = element_text(size = 14, face = "bold")) + 
  theme(plot.title = element_blank())
LabelClusters(p, id = "cell_state", fontface = "bold", size = 7, repel = T)
```

Check cell cycle genes

```{r Cell_cycle_FB, fig.width=5, fig.height=4}
DimPlot(FB, reduction = "umap", shuffle = T,
        group.by = "Phase")
```

```{r DotPlot_markers, fig.width=5, fig.height=6}
DotPlot(FB, assay = "RNA", features = rev(Markers_top3$gene), dot.scale = 5, cluster.idents = FALSE) +
  RotatedAxis() +
  coord_flip() +
  theme(axis.title = element_blank(), axis.text.x = element_text(size = 14), axis.text.y = element_text(size = 13), legend.text = element_text(size = 9), legend.title = element_text(size = 11), plot.margin = unit(c(0, 0, 0, 0.1), 
                           "inches"))
```

```{r VlnPlot_markers_fibro, fig.width=12, fig.height=8}
VlnPlot(FB, features = c("Acta2", "Col1a1", "Col3a1", "Postn", "Vim", "Fn1"), ncol = 3, add.noise = F)
```

```{r VlnPlot_markers_fibro_2, fig.width=16, fig.height=8}
VlnPlot(FB, features = c("Cthrc1", "Tnc", "Spp1", "Timp1", "Tpm2", "Tagln2", "Actg1", "Actb"), ncol = 4, add.noise = F)
```

```{r FeatPlot_markers_fibro, fig.width=15, fig.height=10}
FeaturePlot(FB, features = c("Acta2", "Col1a1", "Col3a1", "Postn", "Vim", "Fn1"), ncol = 3)
```

```{r FeatPlot_Acta2_Group, fig.width=15, fig.height=4}
FeaturePlot(FB, features = c("Acta2"), split.by = "Group", ncol = 4)
```

```{r FeatPlot_Postn_Group, fig.width=15, fig.height=4}
FeaturePlot(FB, features = c("Postn"), split.by = "Group", ncol = 4)
```

```{r FeatPlot_Acta2_Sample, fig.width=15, fig.height=15}
FeaturePlot(FB, features = c("Acta2"), split.by = "Sample") + plot_layout(ncol = 3, nrow = 3)
```

```{r FeatPlot_Postn_Sample, fig.width=15, fig.height=15}
FeaturePlot(FB, features = c("Postn"), split.by = "Sample") + plot_layout(ncol = 3, nrow = 3)
```

```{r VlnPlot_Acta2_FB3_4, fig.width=6, fig.height=4}
VlnPlot(FB, features = "Acta2", idents = c("FB3", "FB4"), group.by = "cell_state", split.by = "Group") + theme(axis.title.x = element_blank()) 
```

```{r VlnPlot_FB3_markers, fig.width=10, fig.height=6}
VlnPlot(FB, features = c("Acta2", "Col1a1", "Col3a1", "Postn", "Vim", "Fn1"), idents = c("FB3"), group.by = "cell_state", split.by = "Group") + theme(axis.title.x = element_blank()) 
```

```{r Barplot_FB_Sample, fig.height=6, fig.width=8, message=FALSE}
color_palette_all <- c("#F8766D", "#00C1AB", "#24B700", "#E18A00", "#00ACFC", "#D575FE", "#BE9C00", "#00BE70", 
                   "#8CAB00", "#00BBDA", "#FF65AC", "#8B93FF", "#EA8331")
color_palette <- c("#F8766D", "#00C1AB", "#24B700", "#E18A00", "#00ACFC", "#D575FE", "#BE9C00")

props <- getTransformedProps(FB$Sample, FB$cell_state, transform="logit")

par(mar = c(5, 5, 3, 11), xpd = TRUE)
barplot(props$Proportions, legend = FALSE, ylab = "Proportions", col = color_palette, 
        cex.names = 2, las = 2, font.lab = 2, font.axis = 2, cex.axis = 1.2, cex.lab = 2)
legend("topright", inset = c(-0.4, 0.1), legend = rownames(props$Proportions), fill = color_palette, bty = "n", cex = 2)
```

```{r Barplot_FB_Group, fig.height=6, fig.width=8, message=FALSE}
color_palette_all <- c("#F8766D", "#00C1AB", "#24B700", "#E18A00", "#00ACFC", "#D575FE", "#BE9C00", "#00BE70", 
                   "#8CAB00", "#00BBDA", "#FF65AC", "#8B93FF", "#EA8331")
color_palette <- c("#F8766D", "#24B700", "#00ACFC")

props <- getTransformedProps(FB$Group, FB$cell_state, transform="logit")

par(mar = c(5, 5, 3, 11), xpd = TRUE)
barplot(props$Proportions, legend = FALSE, ylab = "Proportions", col = color_palette, 
        cex.names = 2, las = 2, font.lab = 2, font.axis = 2, cex.axis = 1.2, cex.lab = 2)
legend("topright", inset = c(-0.39, 0.3), legend = rownames(props$Proportions), fill = color_palette, bty = "n", cex = 2)
```

```{r Barplot_FB_Cell_cycle_cell_state, fig.height=6, fig.width=8, message=FALSE}
color_palette_all <- c("#F8766D", "#00C1AB", "#24B700", "#E18A00", "#00ACFC", "#D575FE", "#BE9C00", "#00BE70", 
                   "#8CAB00", "#00BBDA", "#FF65AC", "#8B93FF", "#EA8331")
color_palette <- c("#F8766D", "#24B700", "#00ACFC")

props <- getTransformedProps(FB$Phase, FB$cell_state, transform="logit")

par(mar = c(5, 5, 3, 11), xpd = TRUE)
barplot(props$Proportions, legend = FALSE, ylab = "Proportions", col = color_palette, 
        cex.names = 2, las = 2, font.lab = 2, font.axis = 2, cex.axis = 1.2, cex.lab = 2)
legend("topright", inset = c(-0.35, 0.3), legend = rownames(props$Proportions), fill = color_palette, bty = "n", cex = 2)
```

```{r Barplot_FB_Cell_cycle_group, fig.height=6, fig.width=8, message=FALSE}
color_palette_all <- c("#F8766D", "#00C1AB", "#24B700", "#E18A00", "#00ACFC", "#D575FE", "#BE9C00", "#00BE70", 
                   "#8CAB00", "#00BBDA", "#FF65AC", "#8B93FF", "#EA8331")
color_palette <- c("#F8766D", "#24B700", "#00ACFC")
FB3 <- subset(FB, cell_state == "FB3")

props <- getTransformedProps(FB3$Phase, FB3$Group, transform="logit")

par(mar = c(7, 5, 3, 11), xpd = TRUE)
barplot(props$Proportions, legend = FALSE, ylab = "Proportions", col = color_palette, 
        cex.names = 2, las = 2, font.lab = 2, font.axis = 2, cex.axis = 1.2, cex.lab = 2)
legend("topright", inset = c(-0.35, 0.3), legend = rownames(props$Proportions), fill = color_palette, bty = "n", cex = 2)
```

```{r Barplot_FB_Cell_state, fig.height=6, fig.width=8, message=FALSE}
color_palette_all <- c("#F8766D", "#00C1AB", "#24B700", "#E18A00", "#00ACFC", "#D575FE", "#BE9C00", "#00BE70", 
                   "#8CAB00", "#00BBDA", "#FF65AC", "#8B93FF", "#EA8331")
color_palette <- c("#F8766D", "#24B700", "#00ACFC", "#E18A00", "#D575FE")

props <- getTransformedProps(FB$cell_state, FB$Group, transform="logit")

par(mar = c(7, 5, 3, 11), xpd = TRUE)
barplot(props$Proportions, legend = FALSE, ylab = "Proportions", col = color_palette, 
        cex.names = 2, las = 2, font.lab = 2, font.axis = 2, cex.axis = 1.2, cex.lab = 2)
legend("topright", inset = c(-0.35, 0.3), legend = rownames(props$Proportions), fill = color_palette, bty = "n", cex = 2)
```

```{r}
df <- Markers[,7:6]
dfsample <- split(df$gene,df$cluster)
length(dfsample)

dfsample$FB1 = bitr(dfsample$FB1, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Mm.eg.db")
dfsample$FB2 = bitr(dfsample$FB2, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Mm.eg.db")
dfsample$FB3 = bitr(dfsample$FB3, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Mm.eg.db")
dfsample$FB4 = bitr(dfsample$FB4, fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Mm.eg.db")

#do the same here, a line like below for each cluster
genelist <- list("FB1" = dfsample$FB1$ENTREZID, 
                 "FB2" = dfsample$FB2$ENTREZID,
                 "FB3" = dfsample$FB3$ENTREZID,
                 "FB4" = dfsample$FB4$ENTREZID
)

# Calculate gene counts across cells
gene_counts <- rowSums(FB@assays$RNA@counts > 0)

# Filter genes to include only those expressed in at least 3 cells
universe_genes <- names(gene_counts[gene_counts >= 3])

# Convert universe gene symbols to Entrez IDs
universe_entrez <- bitr(universe_genes, fromType = "SYMBOL", toType = "ENTREZID", OrgDb = org.Mm.eg.db)$ENTREZID
```

```{r Pathways_GO, fig.height=8, fig.width=6}
GO <- compareCluster(geneCluster = genelist, fun = "enrichGO", ont = "ALL",  OrgDb = "org.Mm.eg.db", universe = universe_entrez)
GO <- gsfilter(GO, by = 'Count', min = 3)
dotplot(GO, label_format = 35, title = "GO Over-representation analysis")
```

```{r Pathways_GO_MF_simplified, fig.height=8, fig.width=6}
GO_simplified <- simplify(
  GO,
  cutoff = 0.5,
  by = "p.adjust",
  select_fun = min,
  measure = "Wang",
  semData = NULL
)
dotplot(GO_simplified, label_format = 35, title = "GO Over-representation analysis")
```

```{r Pathways_KEGG, fig.height=8, fig.width=6}
KEGG <- compareCluster(geneCluster = genelist, fun = "enrichKEGG", organism = 'mmu', universe = universe_entrez)
KEGG <- gsfilter(KEGG, by = 'Count', min = 3)
dotplot(KEGG, label_format = 35, title = "KEGG Pathways")
```


```{r Pathways_REACTOME, fig.height=8, fig.width=6}
REACTOME <- compareCluster(geneCluster = genelist, fun = "enrichPathway", organism = 'mouse', universe = universe_entrez)
REACTOME <- gsfilter(REACTOME, by = 'Count', min = 3)
dotplot(REACTOME, label_format = 40, title = "REACTOME", showCategory = 4)
```

```{r save FB final, eval=FALSE}
saveRDS(FB, 
        here::here(output_dir_data, "FB_no_neuro_epi.rds"))
```

