---
title: "QC_integration_annotation"
author: "GinoBonazza (ginoandrea.bonazza@usz.ch)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: inline
---

```{r knitr config, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(warning = FALSE)

knitr::opts_chunk$set(message = FALSE)

knitr::opts_chunk$set(cache = FALSE)

knitr::opts_chunk$set(dpi = 600, fig.align = "center")
```

## Setup

```{r setup, class.source = "fold-hide"}
# Get current file name to make folder
current_file <- "QC_integration_annotation"

# Load libraries
library(here)
library(readr)
library(readxl)
library(xlsx)
library(Seurat)
library(DropletUtils)
library(Matrix)
library(scDblFinder)
library(scCustomize)
library(dplyr)
library(ggplot2)
library(magrittr)
library(harmony)
library(tidyverse)
library(reshape2)
library(S4Vectors)
library(SingleCellExperiment)
library(pheatmap)
library(png)
library(gridExtra)
library(knitr)
library(scales)
library(RColorBrewer)
library(Matrix.utils)
library(tibble)
library(ggplot2)
library(scater)
library(patchwork)
library(statmod)
library(ArchR)
library(clustree)
library(gprofiler2)

#Output paths
output_dir_data <- here::here("output", current_file)
if (!dir.exists(output_dir_data)) dir.create(output_dir_data)

if (!dir.exists(here::here("docs", "figure"))) dir.create(here::here("docs", "figure"))

output_dir_figs <- here::here("docs", "figure", paste0(current_file, ".Rmd"))
if (!dir.exists(output_dir_figs)) dir.create(output_dir_figs)
```


## Quality Control

Load and merge cellranger output

```{r echo = TRUE, results= "hide"}
EAM_d0_1 <- Read10X(data.dir = here::here("data", "EAMd0"))
EAM_d0_2 <- Read10X(data.dir = here::here("data", "EAMd0F"))
EAM_d19_1 <- Read10X(data.dir = here::here("data", "EAMd19F"))
EAM_d19_2 <- Read10X(data.dir = here::here("data", "EAMd19non_immuno"))
EAM_d19_3 <- Read10X(data.dir = here::here("data", "EAMd19new"))
EAM_d35_1 <- Read10X(data.dir = here::here("data", "EAM35"))
EAM_d35_2 <- Read10X(data.dir = here::here("data", "EAM35c"))

EAM_d0_1_seurat<- CreateSeuratObject(counts = EAM_d0_1, project = "EAM", min.cells = 3, min.features = 200)
EAM_d0_1_seurat <- AddMetaData(object = EAM_d0_1_seurat, metadata = c("d0_1", "d0"), col.name = c("Sample", "Group"))
EAM_d0_2_seurat<- CreateSeuratObject(counts = EAM_d0_2, project = "EAM", min.cells = 3, min.features = 200)
EAM_d0_2_seurat <- AddMetaData(object = EAM_d0_2_seurat, metadata = c("d0_2", "d0"), col.name = c("Sample", "Group"))
EAM_d19_1_seurat<- CreateSeuratObject(counts = EAM_d19_1, project = "EAM", min.cells = 3, min.features = 200)
EAM_d19_1_seurat <- AddMetaData(object = EAM_d19_1_seurat, metadata = c("d19_1", "d19"), col.name = c("Sample", "Group"))
EAM_d19_2_seurat<- CreateSeuratObject(counts = EAM_d19_2, project = "EAM", min.cells = 3, min.features = 200)
EAM_d19_2_seurat <- AddMetaData(object = EAM_d19_2_seurat, metadata = c("d19_2", "d19"), col.name = c("Sample", "Group"))
EAM_d19_3_seurat<- CreateSeuratObject(counts = EAM_d19_3, project = "EAM", min.cells = 3, min.features = 200)
EAM_d19_3_seurat <- AddMetaData(object = EAM_d19_3_seurat, metadata = c("d19_3", "d19"), col.name = c("Sample", "Group"))
EAM_d35_1_seurat<- CreateSeuratObject(counts = EAM_d35_1, project = "EAM", min.cells = 3, min.features = 200)
EAM_d35_1_seurat <- AddMetaData(object = EAM_d35_1_seurat, metadata = c("d35_1", "d35"), col.name = c("Sample", "Group"))
EAM_d35_2_seurat<- CreateSeuratObject(counts = EAM_d35_2, project = "EAM", min.cells = 3, min.features = 200)
EAM_d35_2_seurat <- AddMetaData(object = EAM_d35_2_seurat, metadata = c("d35_2", "d35"), col.name = c("Sample", "Group"))
rm(EAM_d0_1, EAM_d0_2, EAM_d19_1, EAM_d19_2, EAM_d19_3, EAM_d35_1, EAM_d35_2)

EAM_preQC <- merge(EAM_d0_1_seurat, y = c(EAM_d0_2_seurat, EAM_d19_1_seurat, EAM_d19_2_seurat, EAM_d19_3_seurat, EAM_d35_1_seurat, EAM_d35_2_seurat), 
                   add.cell.ids = c("EAM_d0_1", "EAM_d0_2", "EAM_d19_1", "EAM_d19_2", "EAM_d19_3", "EAM_d35_1", "EAM_d35_2"))
rm(EAM_d0_1_seurat, EAM_d0_2_seurat, EAM_d19_1_seurat, EAM_d19_2_seurat, EAM_d19_3_seurat, EAM_d35_1_seurat, EAM_d35_2_seurat)
```

Add metadata: percentage of mitochondrial and ribosomal genes

```{r}
EAM_preQC[["percent.mt"]] <- PercentageFeatureSet(EAM_preQC, pattern = "^mt-")
EAM_preQC[["percent.rp"]] <- PercentageFeatureSet(EAM_preQC, pattern = "^Rp[sl]")
```

Check quality control parameters

```{r QC_pre_VlnPlots, fig.height=6, fig.width=8}
p1 <- VlnPlot(EAM_preQC, features = "nCount_RNA", group.by = "Sample", pt.size = 0) + theme(axis.title.x = element_blank()) + NoLegend()

p2 <- VlnPlot(EAM_preQC, features = "nFeature_RNA", group.by = "Sample", pt.size = 0) + theme(axis.title.x = element_blank()) + NoLegend()

p3 <- VlnPlot(EAM_preQC, features = "percent.mt", group.by = "Sample", pt.size = 0) + theme(axis.title.x = element_blank()) + NoLegend()

p4 <- VlnPlot(EAM_preQC, features = "percent.rp", group.by = "Sample", pt.size = 0) + theme(axis.title.x = element_blank()) + NoLegend()

QC_pre_VlnPlots <- p1 + p2 + p3 + p4 + plot_layout(ncol = 2)

QC_pre_VlnPlots
```

```{r QC_pre_VlnPlots_zoom, fig.height=10, fig.width=8}
p1 <- VlnPlot(EAM_preQC, features = "nCount_RNA", group.by = "Sample", pt.size = 0, y.max = 20000) + theme(axis.title.x = element_blank()) + NoLegend()

p2 <- VlnPlot(EAM_preQC, features = "nFeature_RNA", group.by = "Sample", pt.size = 0, y.max = 5000) + theme(axis.title.x = element_blank()) + NoLegend()

p3 <- VlnPlot(EAM_preQC, features = "percent.mt", group.by = "Sample", pt.size = 0, y.max = 25) + theme(axis.title.x = element_blank()) + NoLegend()

p4 <- VlnPlot(EAM_preQC, features = "percent.rp", group.by = "Sample", pt.size = 0, y.max = 50) + theme(axis.title.x = element_blank()) + NoLegend()

QC_pre_VlnPlots_zoom <- p1 + p2 + p3 + p4 + plot_layout(ncol = 2)

QC_pre_VlnPlots_zoom
```

Doublets detection

```{r}
EAM_preQC_sce <- as.SingleCellExperiment(EAM_preQC)
EAM_preQC_sce <- scDblFinder(EAM_preQC_sce, samples="Sample", clusters = TRUE)
table(EAM_preQC_sce@colData$scDblFinder.class)
EAM_preQC <- as.Seurat(EAM_preQC_sce, counts = "counts", data = "logcounts")
rm(EAM_preQC_sce)
EAM_preQC@meta.data[EAM_preQC@meta.data$scDblFinder.class %in% "singlet", "scDblFinder.n"] = paste0("Singlets (n=", table(EAM_preQC$scDblFinder.class)[1], ")")
EAM_preQC@meta.data[EAM_preQC@meta.data$scDblFinder.class %in% "doublet", "scDblFinder.n"] = paste0("Doublets (n=", table(EAM_preQC$scDblFinder.class)[2], ")")
EAM_preQC$scDblFinder.n <- factor(x = EAM_preQC$scDblFinder.n, levels = c(rownames(table(EAM_preQC$scDblFinder.n))[2], rownames(table(EAM_preQC$scDblFinder.n))[1])) 
```

```{r QC_pre_Doublets, fig.height=3, fig.width=8}
p1 <- VlnPlot(EAM_preQC, features = c("nCount_RNA"), split.by = "scDblFinder.n", group.by = "Sample", pt.size = 0, y.max = 50000) + theme(axis.title.x = element_blank()) + NoLegend()

p2 <- VlnPlot(EAM_preQC, features = c("nFeature_RNA"), split.by = "scDblFinder.n", group.by = "Sample", pt.size = 0, y.max = 10000) + theme(axis.title.x = element_blank()) 

QC_pre_Doublets <- p1 + p2 + plot_layout(ncol = 2)

QC_pre_Doublets
```

```{r eval=FALSE}
saveRDS(EAM_preQC, 
        here::here(output_dir_data, "EAM_preQC.rds"))
```

Remove doublets

```{r EAM_preQC_no_doublets}
EAM_preQC_no_doublets <- subset(x = EAM_preQC, subset = scDblFinder.class == "singlet")
table(EAM_preQC_no_doublets@meta.data$scDblFinder.class)
rm(EAM_preQC)
```

Check quality control parameters after removing doublets

```{r QC_pre_no_doublets_VlnPlots, fig.height=6, fig.width=8}
p1 <- VlnPlot(EAM_preQC_no_doublets, features = "nCount_RNA", group.by = "Sample", pt.size = 0) + theme(axis.title.x = element_blank()) + NoLegend()

p2 <- VlnPlot(EAM_preQC_no_doublets, features = "nFeature_RNA", group.by = "Sample", pt.size = 0) + theme(axis.title.x = element_blank()) + NoLegend()

p3 <- VlnPlot(EAM_preQC_no_doublets, features = "percent.mt", group.by = "Sample", pt.size = 0) + theme(axis.title.x = element_blank()) + NoLegend()

p4 <- VlnPlot(EAM_preQC_no_doublets, features = "percent.rp", group.by = "Sample", pt.size = 0) + theme(axis.title.x = element_blank()) + NoLegend()

QC_pre_no_doublets_VlnPlots <- p1 + p2 + p3 + p4 + plot_layout(ncol = 2)

QC_pre_no_doublets_VlnPlots
```

```{r QC_pre_no_doublets_VlnPlots_zoom, fig.height=10, fig.width=8}
p1 <- VlnPlot(EAM_preQC_no_doublets, features = "nCount_RNA", group.by = "Sample", pt.size = 0, y.max = 20000) + theme(axis.title.x = element_blank()) + NoLegend()

p2 <- VlnPlot(EAM_preQC_no_doublets, features = "nFeature_RNA", group.by = "Sample", pt.size = 0, y.max = 5000) + theme(axis.title.x = element_blank()) + NoLegend()

p3 <- VlnPlot(EAM_preQC_no_doublets, features = "percent.mt", group.by = "Sample", pt.size = 0, y.max = 25) + theme(axis.title.x = element_blank()) + NoLegend()

p4 <- VlnPlot(EAM_preQC_no_doublets, features = "percent.rp", group.by = "Sample", pt.size = 0, y.max = 50) + theme(axis.title.x = element_blank()) + NoLegend()

QC_pre_no_doublets_VlnPlots_zoom <- p1 + p2 + p3 + p4 + plot_layout(ncol = 2)

QC_pre_no_doublets_VlnPlots_zoom
```

Filter based on number of counts, features and percentage of mitochondrial genes

```{r}
EAM <- subset(EAM_preQC_no_doublets, subset = 
                nFeature_RNA > 200 &
                percent.mt < 25 &
                nCount_RNA > 500)

table(EAM$Sample)
rm(EAM_preQC_no_doublets)
```

Check quality control parameters

```{r QC_post_VlnPlots, fig.height=6, fig.width=8}
p1 <- VlnPlot(EAM, features = "nCount_RNA", group.by = "Sample", pt.size = 0) + theme(axis.title.x = element_blank()) + NoLegend()

p2 <- VlnPlot(EAM, features = "nFeature_RNA", group.by = "Sample", pt.size = 0) + theme(axis.title.x = element_blank()) + NoLegend()

p3 <- VlnPlot(EAM, features = "percent.mt", group.by = "Sample", pt.size = 0) + theme(axis.title.x = element_blank()) + NoLegend()

p4 <- VlnPlot(EAM, features = "percent.rp", group.by = "Sample", pt.size = 0) + theme(axis.title.x = element_blank()) + NoLegend()

QC_post_VlnPlots <- p1 + p2 + p3 + p4 + plot_layout(ncol = 2)

QC_post_VlnPlots
```

```{r QC_post_VlnPlots_zoom, fig.height=10, fig.width=8}
p1 <- VlnPlot(EAM, features = "nCount_RNA", group.by = "Sample", pt.size = 0, y.max = 20000) + theme(axis.title.x = element_blank()) + NoLegend()

p2 <- VlnPlot(EAM, features = "nFeature_RNA", group.by = "Sample", pt.size = 0, y.max = 5000) + theme(axis.title.x = element_blank()) + NoLegend()

p3 <- VlnPlot(EAM, features = "percent.mt", group.by = "Sample", pt.size = 0, y.max = 25) + theme(axis.title.x = element_blank()) + NoLegend()

p4 <- VlnPlot(EAM, features = "percent.rp", group.by = "Sample", pt.size = 0, y.max = 50) + theme(axis.title.x = element_blank()) + NoLegend()

QC_post_VlnPlots_zoom <- p1 + p2 + p3 + p4 + plot_layout(ncol = 2)

QC_post_VlnPlots_zoom
```


## Integration and clustering

Normalization and scaling.

```{r eval=FALSE}
DefaultAssay(EAM) <- "RNA"
EAM_not_integrated <- EAM %>%
    NormalizeData() %>%
    FindVariableFeatures(selection.method = "vst", nfeatures = 2000) %>% 
    ScaleData(features = rownames(EAM), vars.to.regress = "percent.mt")
```

PCA 

```{r, eval=FALSE, include=FALSE}
EAM_not_integrated <- RunPCA(EAM_not_integrated, npcs = 50)
```

```{r eval=FALSE}
saveRDS(EAM_not_integrated, 
        here::here(output_dir_data, "EAM_not_integrated.rds"))
```

```{r}
EAM_not_integrated <- readRDS(here::here(output_dir_data, "EAM_not_integrated.rds"))
```


```{r Elbow_not_integrated, fig.width=4, fig.height=4}
ElbowPlot(EAM_not_integrated, ndims = 50)
```

Clustering without integration

```{r eval=FALSE}
EAM_not_integrated <- RunUMAP(EAM_not_integrated, dims = 1:40)
EAM_not_integrated <- FindNeighbors(EAM_not_integrated, dims = 1:40)
EAM_not_integrated <- FindClusters(EAM_not_integrated, resolution = seq(0.1, 0.8, by=0.1))
```

```{r Clustree_not_integrated, fig.width=6, fig.height=9}
clustree::clustree(EAM_not_integrated@meta.data[,grep("RNA_snn_res", colnames(EAM_not_integrated@meta.data))],
                   prefix = "RNA_snn_res.")
```

```{r UMAPs_not_integrated, fig.width=14, fig.height=4}
DimPlot(EAM_not_integrated, reduction = "umap", shuffle = T,
        group.by = c("RNA_snn_res.0.2", "Sample", "Group"), ncol = 3)
```

```{r eval=FALSE}
saveRDS(EAM_not_integrated, 
        here::here(output_dir_data, "EAM_not_integrated.rds"))
```

Integrate the samples using Harmony

```{r eval=FALSE}
EAM_integrated <- RunHarmony(EAM_not_integrated, assay.use="RNA", group.by.vars = "Sample", dims.use = 1:50)
```

```{r eval=FALSE}
EAM_integrated <- RunUMAP(EAM_integrated, dims = 1:30, reduction = "harmony")
EAM_integrated <- FindNeighbors(EAM_integrated, dims = 1:30, reduction = "harmony")
EAM_integrated <- FindClusters(EAM_integrated, resolution = seq(0.1, 0.8, by=0.1))
```

```{r eval=FALSE}
saveRDS(EAM_integrated, 
        here::here(output_dir_data, "EAM_integrated.rds"))
```

```{r}
EAM_integrated <- readRDS(here::here(output_dir_data, "EAM_integrated.rds"))
```

```{r Clustree_integrated, fig.width=6, fig.height=9}
clustree::clustree(EAM_integrated@meta.data[,grep("RNA_snn_res", colnames(EAM_integrated@meta.data))],
                   prefix = "RNA_snn_res.")
```

```{r UMAPs_integrated, fig.width=14, fig.height=4}
DimPlot(EAM_integrated, reduction = "umap", shuffle = T,
        group.by = c("RNA_snn_res.0.2", "Sample", "Group"), ncol = 3, label = T)
```

Find the markers that characterize each cell population

```{r}
DefaultAssay(EAM_integrated) <- "RNA"
Idents(EAM_integrated) <- "RNA_snn_res.0.2"
Markers <- FindAllMarkers(EAM_integrated, only.pos = TRUE, min.pct = 0.5, logfc.threshold = 0.5)
write.csv(Markers, here::here(output_dir_data, "EAM_Markers_all.csv"))
Markers_top10 <- as.data.frame(Markers %>% group_by(cluster) %>% top_n(n = 10, wt = avg_log2FC))
write.csv(Markers_top10, here::here(output_dir_data, "EAM_Markers_top10.csv"))
Markers_top3 <- as.data.frame(Markers %>% group_by(cluster) %>% top_n(n = 3, wt = avg_log2FC))
write.csv(Markers_top3, here::here(output_dir_data, "EAM_Markers_top3.csv"))
```

```{r Heatmap_low_quality, fig.width=15, fig.height=10}
mapal <- colorRampPalette(RColorBrewer::brewer.pal(9,"RdBu"))(256)
mapal <- rev(mapal[1:256])
Heatmap <- DoHeatmap(EAM_integrated, draw.line = F, features = Markers_top10$gene) +
  scale_fill_gradientn(colours = mapal) +
  theme(text = element_text(size = 15), axis.text.y = element_text(size = 5)) +
  theme(plot.margin = unit(c(0.1, 0, 0, 0), 
                           "inches"))
Heatmap
```

Check QC parameters in each cluster

```{r QC_VlnPlots_low_quality, fig.width=10, fig.height=6}
VlnPlot(EAM_integrated, features = c("nCount_RNA", "nFeature_RNA", "percent.mt", "percent.rp"), ncol = 2, pt.size = 0)
```

Check cell cycle genes

```{r Cell_cycle_UMAP, fig.width=5, fig.height=4}
DefaultAssay(EAM_integrated) <- "RNA"
mmus_s = gorth(cc.genes.updated.2019$s.genes, source_organism = "hsapiens", target_organism = "mmusculus")$ortholog_name
mmus_g2m = gorth(cc.genes.updated.2019$g2m.genes, source_organism = "hsapiens", target_organism = "mmusculus")$ortholog_name
EAM_integrated <- CellCycleScoring(EAM_integrated, s.features = mmus_s, g2m.features = mmus_g2m)
DimPlot(EAM_integrated, reduction = "umap", shuffle = T,
        group.by = "Phase")
```


## Cell type annotation

Annotate the clusters based on the characteristic markers

```{r}
EAM_integrated@meta.data[EAM_integrated@meta.data$RNA_snn_res.0.2 %in% c("0", "3", "4", "11"), "cell_type"] = "T-cells"
EAM_integrated@meta.data[EAM_integrated@meta.data$RNA_snn_res.0.2 %in% c("1"), "cell_type"] = "B-cells"
EAM_integrated@meta.data[EAM_integrated@meta.data$RNA_snn_res.0.2 %in% c("2"), "cell_type"] = "Fibroblasts"
EAM_integrated@meta.data[EAM_integrated@meta.data$RNA_snn_res.0.2 %in% c("5", "6", "8"), "cell_type"] = "Myeloid cells"
EAM_integrated@meta.data[EAM_integrated@meta.data$RNA_snn_res.0.2 %in% c("7"), "cell_type"] = "Proliferating lymphocytes"
EAM_integrated@meta.data[EAM_integrated@meta.data$RNA_snn_res.0.2 %in% c("9"), "cell_type"] = "NK-cells"
EAM_integrated@meta.data[EAM_integrated@meta.data$RNA_snn_res.0.2 %in% c("10"), "cell_type"] = "Endothelial cells"
EAM_integrated@meta.data[EAM_integrated@meta.data$RNA_snn_res.0.2 %in% c("12"), "cell_type"] = "CMs"
EAM_integrated@meta.data[EAM_integrated@meta.data$RNA_snn_res.0.2 %in% c("13"), "cell_type"] = "Mesothelial cells"
EAM_integrated@meta.data[EAM_integrated@meta.data$RNA_snn_res.0.2 %in% c("14"), "cell_type"] = "SMC"
EAM_integrated@meta.data[EAM_integrated@meta.data$RNA_snn_res.0.2 %in% c("15"), "cell_type"] = "Platelets"

EAM_integrated$cell_type <- factor(EAM_integrated$cell_type, levels = c("T-cells", 
                                                                        "B-cells",
                                                                        "Fibroblasts",
                                                                        "Myeloid cells",
                                                                        "Proliferating lymphocytes",
                                                                        "NK-cells",
                                                                        "Endothelial cells",
                                                                        "CMs",
                                                                        "Mesothelial cells",
                                                                        "SMC",
                                                                        "Platelets"))
Idents(EAM_integrated) <- EAM_integrated$cell_type
```

```{r FindAllMarkers cell_type}
DefaultAssay(EAM_integrated) <- "RNA"
Idents(EAM_integrated) <- "cell_type"
Markers <- FindAllMarkers(EAM_integrated, only.pos = TRUE, min.pct = 0.5, logfc.threshold = 0.5)
write.csv(Markers, here::here(output_dir_data, "EAM_Markers_all_cell_type.csv"))
Markers_top10 <- as.data.frame(Markers %>% group_by(cluster) %>% top_n(n = 10, wt = avg_log2FC))
write.csv(Markers_top10, here::here(output_dir_data, "EAM_Markers_top10_cell_type.csv"))
Markers_top3 <- as.data.frame(Markers %>% group_by(cluster) %>% top_n(n = 3, wt = avg_log2FC))
write.csv(Markers_top3, here::here(output_dir_data, "EAM_Markers_top3_cell_type.csv"))
```

```{r Heatmap, fig.width=12, fig.height=8}
Heatmap <- DoHeatmap(EAM_integrated, label = FALSE, draw.line = F, features = Markers_top10$gene) + 
  scale_fill_gradientn(colours = mapal) +
  theme(text = element_text(size = 12), 
        axis.text.y = element_text(size = 4.5)) +
  theme(plot.margin = unit(c(0, 0, 0, 0), "inches")) +
  guides(fill = guide_colorbar(barwidth = 1, barheight = 4))
Heatmap
```

```{r UMAP_cell_type, fig.width=6.5, fig.height=6}
p <- DimPlot(EAM_integrated, group.by = "cell_type", reduction = "umap", label = F) + 
  NoLegend() + 
  theme(axis.text=element_text(size=10, face = "bold"), axis.title = element_text(size = 14, face = "bold")) + 
  theme(plot.title = element_blank())
LabelClusters(p, id = "cell_type", fontface = "bold", size = 5, repel = T)
```

```{r DotPlot_markers, fig.width=8, fig.height=12}
DotPlot(EAM_integrated, assay = "RNA", features = rev(Markers_top3$gene), dot.scale = 5, cluster.idents = FALSE) +
  RotatedAxis() +
  coord_flip() +
  theme(axis.title = element_blank(), axis.text.x = element_text(size = 14), axis.text.y = element_text(size = 13), legend.text = element_text(size = 9), legend.title = element_text(size = 11), plot.margin = unit(c(0, 0, 0, 0.1), 
                           "inches"))
```

```{r FeatPlot_markers, fig.width=12, fig.height=8}
FeaturePlot(EAM_integrated, features = c("Cd3e", "Ms4a1", "Col1a1", "Cxcl2", "Mki67", "Nkg7", "Ptprb", "Tnnt2", "Msln", "Rgs5", "Ppbp"), ncol = 4)
```

```{r FeatPlot_markers_fibro, fig.width=15, fig.height=10}
FeaturePlot(EAM_integrated, features = c("Acta2", "Col1a1", "Col3a1", "Postn", "Vim", "Fn1"), ncol = 3)
```

```{r FeatPlot_markers_fibro_2, fig.width=15, fig.height=10}
FeaturePlot(subset(EAM_integrated, cell_type == "Fibroblasts"), features = c("Acta2", "Col1a1", "Col3a1", "Postn", "Vim", "Fn1"), ncol = 3)
```

```{r FeatPlot_Acta2_Group, fig.width=15, fig.height=5}
FeaturePlot(subset(EAM_integrated, cell_type == "Fibroblasts"), features = c("Acta2"), split.by = "Group", ncol = 3)
```

```{r FeatPlot_Postn_Group, fig.width=15, fig.height=5}
FeaturePlot(subset(EAM_integrated, cell_type == "Fibroblasts"), features = c("Postn"), split.by = "Group", ncol = 3)
```

```{r FeatPlot_Acta2_Sample, fig.width=15, fig.height=15}
FeaturePlot(subset(EAM_integrated, cell_type == "Fibroblasts"), features = c("Acta2"), split.by = "Sample") + plot_layout(ncol = 3, nrow = 3)
```

```{r FeatPlot_Postn_Sample, fig.width=15, fig.height=15}
FeaturePlot(subset(EAM_integrated, cell_type == "Fibroblasts"), features = c("Postn"), split.by = "Sample") + plot_layout(ncol = 3, nrow = 3)
```

```{r save EAM_integrated final, eval = FALSE}
saveRDS(EAM_integrated, 
        here::here(output_dir_data, "EAM_integrated.rds"))
```
